True versus apparent shapes of astrophysical bow shocks

### 2017-05-23 papers/Paper1/sec-quadrics-observations.tex
Add a better abstract to the quadrics paper
This was originally written for the Grazyna Puebla conference
Change significance levels in p-value histogram fig
Lower value is now p=0.003, corresponding to approx 3-sigma

\newcommand\hii{\ion{H}{ii}}

@@

We now investigate if the bow shock shapes of the MIPSGAL sources are
correlated with any other parameters via the following methodology:
\begin{enumerate}[1.]
\item For each of the parameters in the \citet{Kobulnicky:2016a}
  catalog, we divide the sources into two or more sub-samples,
  according to the value of the parameter.  For quantitative
  parameters, such as those discussed in the previous section, we use
  two sub-samples of equal size, with membership determined by whether
  the parameter is larger or smaller than the median value.  But we
  also use categorical parameters, such as the type of bow shock
  environment, or the presence/absence of \SI{8}{\um} emission, in
  which case the sub-samples are of unequal size.
\item We plot the KDEs of the two sub-samples separately on the
  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
  differences.
\item We test if there is any statistically significant difference
  between the bow shock shapes of the sub-samples by applying the
  two-sample Anderson--Darling test \citep{Anderson:1952a,
    Scholz:1987a, Makarov:2017a} to \(R_c/R_0\) and \(R_{90}/R_0\)
  separately.  This is a non-parametric test of the \textit{null
    hypothesis} that the two sub-samples are drawn from the same
  distribution.  It returns a \(p\)-value, which is the estimated
  probability that the observed difference between the two sub-samples
  would be as large as it is purely by chance if they were all were
  drawn from the same distribution.  We adopt a threshold of
  \(p < 0.001\) in order to confidently reject the null hypothesis and
  declare a ``significant'' difference between the two sub-samples,
  but we also consider the less strict threshold of \(p < 0.05\) as an
  indicator of ``probable'' difference (see
  Appendix~\ref{sec:distr-p-values} for details).
\end{enumerate}

>>>>

@@

We now investigate if the bow shock shapes of the MIPSGAL sources are
correlated with any other parameters via the following methodology:
\begin{enumerate}[1.]
\item For each of the parameters in the \citet{Kobulnicky:2016a}
  catalog, we divide the sources into two or more sub-samples,
  according to the value of the parameter.  For quantitative
  parameters, such as those discussed in the previous section, we use
  two sub-samples of equal size, with membership determined by whether
  the parameter is larger or smaller than the median value.  But we
  also use categorical parameters, such as the type of bow shock
  environment, or the presence/absence of \SI{8}{\um} emission, in
  which case the sub-samples are of unequal size.
\item We plot the KDEs of the two sub-samples separately on the
  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
  differences.
\item We check if there is any statistically significant difference
  between the bow shock shapes of the sub-samples by applying three
  different non-parametric tests to \(R_c/R_0\) and \(R_{90}/R_0\)
  separately.  The principal test used is the two-sample
  Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a,
    Makarov:2017a}, which is a general test of the \textit{null
    hypothesis} that the two sub-samples are drawn from the same
  distribution.  It returns a \(p\)-value, which is the estimated
  probability that the observed difference between the two sub-samples
  would be as large as it is purely by chance if they were all were
  drawn from the same distribution.  We consider two different
  thresholds for significance: \(p < 0.05\) (approximately
  2-\(\sigma\) for a normal distribution) and \(p < 0.003\) (approximately
  3-\(\sigma\)).  We show in Appendix~\ref{sec:distr-p-values} that the
  more stringent \(p < 0.003\) condition is required in order to
  confidently reject the null hypothesis and declare a ``significant''
  difference between the two sub-samples, but we also consider the
  less strict threshold of \(p < 0.05\) as an indicator of
  ``possible'' difference.  We supplement the general-purpose
  Anderson--Darling test with two tests that probe specific features of
  the sample distributions: the Mann--Whitney--Wilcoxon \(U\) test
  \citep{Mann:1947a}, which is sensitive to differences in the central
  value (e.g., median) and the Brown--Forsythe test
  \citep{Brown:1974a}, which is sensitive to differences in the
  variance, or width, of the distribution (see
  Appendix~\ref{sec:distr-p-values} for details).
\end{enumerate}
